\documentclass[11pt]{tracv}
%\addtolength{\topmargin}{+2cm}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{enumitem}
\frenchspacing

\name{Ganan Jeyakumar}
%\address{123 Pacific Drive \\ Fitzherbert}{Palmerston North, 4410}{New Zealand}{\vspace{-11pt}}
\address{4A Valley Road \\ Northcote}{Auckland, 0626}{New Zealand}{\vspace{0pt}}
\phone{\href{tel:+64224020106}{+64 22 402 0106}}
\email{gnanjeya@icloud.com}
\website{www.gananjeya.com}

%\def\labelitemi{--}

\begin{document}

\null

\head

\begin{columnsection}{Education}

	\columnentry{BSc in Data Science}{The University of Auckland}{March 2014 -- Present}{Auckland, New Zealand}{\vspace{3pt} Coursework in: Computer Science, Electrical \& Computer Engineering, Statistics and Mathematics}{}{}

%	\columnentry{BE(Hons) in Computer and Systems Engineering}{The University of Auckland}{March 2014 -- November 2015 (incomplete)}{Auckland, New Zealand}{}{}{}

%	\columnentry{NCEA Level 3}{Palmerston North Boys' High School}{Achieved with Merit}{Palmerston North, New Zealand}{}{}{}

%    \columnentry{IGCSE}{Palmerston North Boys' High School}{Mathematics, Physics, Chemistry, Biology}{Palmerston North, New Zealand}{}{}{}

\end{columnsection}

\begin{columnsection}{Work Experience}

	\columnentry{Group Services Administrator}{The University of Auckland}{School of Medical Sciences}{Auckland, New Zealand}{Manager: Kathryn Siow}{August 2018 -- Present}{
	\vspace{3pt}
	Responsibilities:
	\vspace{-3pt}
	\begin{itemize}[noitemsep]
	
	\item[$\triangleright$] Devising and implementing IT strategy for the delivery of teaching and assessment to students
	\item[$\triangleright$] Providing the necessary training and support to the staff who are using these technologies
	
	\end{itemize}}
	
	\columnentry{Practicum Placement Coordinator}{The University of Auckland}{School of Pharmacy}{Auckland, New Zealand}{Manager: Kathryn Siow}{August 2019 -- February 2020}{}
	
	\columnentry{Photographer}{Shadows Productions NZ}{Event Photography}{Auckland, New Zealand}{\url{www.shadowsproductions.com}}{January 2017 -- Present}{}	
	
	\columnentry{Telephone Interviewer}{Ipsos Limited}{Call Centre}{Auckland, New Zealand}{Manager: Sue Bowerbank}{April 2018 -- July 2018}{}
	
%	\columnentry{Product Manager}{Overlake Technologies}{Postvites Web Application}{Bellevue, USA}{\href{http://postvites.com}{www.postvites.com}}{December 2017 -- March 2018}{}

	\columnentry{Laboratory Technician}{The University of Melbourne}{Melbourne Networked Society Institute}{Melbourne, Australia}{Supervisor: Prof Thas A. Nirmalathas}{January 2017 -- March 2017}{}

	\columnentry{Research Assistant}{The University of Melbourne}{Experimental Condensed Matter Physics}{Melbourne, Australia}{Supervisor: Dr Kumaravelu Ganesan}{November 2016 -- December 2016}{}

	\columnentry{Research Assistant}{The University of Melbourne}{The Bionics Institute}{Melbourne, Australia}{Supervisor: Dr David Garrett}{November 2015 -- December 2015}{}

	\columnentry{Assistant Product Development Engineer}{Fisher \& Paykel Healthcare}{Neo Dev-Respiratory Team}{Auckland, New Zealand}{Manager: Jacky Cheung}{November 2014 -- February 2015}{}

\end{columnsection}

%\begin{columnsection}{Research Experience}

%	  \columnentry{Manawatu Science and Technology Fair}{Palmerston North Boys' High School}{Plant \& Food Research Laboratory}{Palmerston North, New Zealand}{Mentor: Mrs Anna Fletcher}{February 2013 -- August 2013}{}

%	  \columnentry{Silver CREST NZ Research Project}{Plant \& Food Research}{Sustainability Production and Footprint Team}{Palmerston North, New Zealand}{Mentors:  Dr Markus Deurer and Dr Brent Clothier}{March 2011 -- May 2013}{}

%	  \columnentry{NCEA Level 3 Chemistry Research Project}{Palmerston North Boys' High School}{Effect of UV light exposture on Vitamin C levels in orange juice}{Palmerston North, New Zealand}{Mentor:  Mrs Sue Taylor (HOD of Chemistry)}{March 2011--May 2013}{}

%\end{columnsection}

%\begin{columnsection}{Teaching Experience}
%
%
%
%   	 \columnentry{Tutor}{Palmerston North Boys' High School}{2013 NZ Brain Bee Challenge National Team}{Palmerston North, New Zealand}{Biology and Chemistry Departments}{March 2013 -- July 2013}{}
%
%\end{columnsection}

%\begin{hangingsection}{Presentations}
%
%        \hangingentry \textbf{Bilge, A. D.} (July 2012). Investigating evolution via computational biology: The application of phylogenetic analyses to epidemiology and ecology. \emph{XSEDE12}, Chicago, IL. Invited; received NSF funding for travel and lodging.
%
%\end{hangingsection}

%\begin{hangingsection}{Sporting Achievements}
%
%	\hangingentry \textbf{Bronze at NZ U16 Waterpolo Championships}, Palmerston North Boys' High School U16A Team~(July 2013).
%
%\end{hangingsection}

\pagebreak

\begin{hangingsection}{Projects}
	
	\hangingentry Installation and configuration of a local area network to reduce latency of multimedia content. \textit{Technologies used: power-line networking, web-managed switch, multi-user MIMO, DHCP.}
	
	\hangingentry Designed and built personal website. \textit{Technologies used: GitHub, Cloudflare DNS, HTML, JavaScript, CSS.}
	
	\hangingentry Administered server for conferencing webapp with automated mail delivery service. \\ \textit{Technologies used: Ruby on Rails, PostgreSQL, Heroku, SMTP, DMARC, Google Analytics.}
	
	\hangingentry Installation of Linux on high performance machine for scientific computing. Configuration of file system and hardware drivers. \textit{Technologies used: Ubuntu OS, GRUB, ext4, Bash, OpenCL.}
	
	\hangingentry Designed nested RAID system composed of network-attached storage. Implementation pending.
	
	\hangingentry Installation of Windows software and operating systems on various hardware. \\ \textit{Technologies used: Windows 8, 10 and Server, BIOS.}
	
\end{hangingsection}

\begin{hangingsection}{Honours and Awards}

	\hangingentry \textbf{\$6000 Scholarship}, The University of Auckland Jubilee Awards~(October, 2013).

	\hangingentry \textbf{Silver Barrowclough Award}, Palmerston North Boys' High School~(November 2012).

%	\hangingentry \textbf{7 Individual Awards Winner}, Manawatu Science and Technology Fair~(August 2013).\\
%		\begin{itemize}
%		\item Fonterra High Distinction
%		\item AgResearch Prize
%		\item Agresearch Internship
%		\item New Zealand Institute of Agricultural and Horticultural Science Prize
%		\item Landcare Research Environment Prize and Internship
%		\item Australian Institute of Mining and Metallurgy Prize
%		\item DairyNZ Prize
%		\end{itemize}
%
%	\hangingentry \textbf{North Island Brain Bee Challenge}, Palmerston North Boys' High School~(2012).

\end{hangingsection}

\begin{columnsection}{Service}

	\columnentry{Undergraduate Student Representative}{The University of Auckland}{Residential Advisory Committee}{Auckland, New Zealand}{Carlaw Park Student Village}{March 2015 -- November 2015}{}

	 \columnentry{Tutor}{Palmerston North Boys' High School}{Junior School Academic Assistance}{Palmerston North, New Zealand}{Chemistry Department}{February 2013 -- October 2013}{}

%	\hangingentry \textbf{Odyssey Design Challenge}, Engineering Without Borders (EWB) -- Community Service~(2014).

%    \hangingentry \textbf{Construct Presentation for Toastmasters New Zealand National Convention 2013}, Toastmasters International -- Volunteer~(May 2013).

\end{columnsection}

%\begin{hangingsection}{Presentations}
%
%        \hangingentry \textbf{Bilge, A. D.} (July 2012). Investigating evolution via computational biology: The application of phylogenetic analyses to epidemiology and ecology. \emph{XSEDE12}, Chicago, IL. Invited; received NSF funding for travel and lodging.
%
%\end{hangingsection}

%\begin{columnsection}{Referees}
%
%\begin{multicols}{2}
%
%	Dr David Garrett\\
%	ARC DECRA Fellow\\
%	Department of Physics\\
%	The University of Melbourne\\
%	Parkville VIC 3010, Australia\\
%	\texttt{dgarrett@unimelb.edu.au}\\
%	Ph: +61 3 9035 4973\\
%	Mob: +61 4 0335 3730\\
%
%	\vspace{0.25cm}
%
%    	Jacky Cheung\\
%	Senior Product Development Engineer\\
%%	Systems Modelling\\
%	Fisher \& Paykel Healthcare Limited\\
%	15 Maurice Paykel Place, Auckland 2013\\
%	\texttt{Jacky.Cheung@fphcare.co.nz}\\
%%	+64 6 953 7687, +64 21 226 8687\\
%
%	\vspace{0.25cm}
%	\columnbreak
%
%	Ivan Teng\\
%	Senior Product Development Engineer\\
%	RAC (Respiratory and Acute Care)\\
%	Fisher \& Paykel Healthcare Limited\\
%	15 Maurice Paykel Place, Auckland 2013\\
%	\texttt{Ivan.Teng@fphcare.co.nz}\\
%	+64 9 574 0123 ext 8090\\
%
%\end{multicols}
%
%\end{columnsection}

\end{document}
